---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    smooth_scroll: true
    css: style.css
    theme: cosmo
    self_contained: false
    mathjax: NULL
params:
  custom_title: "Administrative summary"
title: "`r params$custom_title`"
---

<style>                     
.navbar {
  background-color:#5A0A69;
  border-color:black;
}
#dashboard-container { 
  all: initial !important; 
}
</style>

Row
-------------------------------------

### `r i18n$t("country_reporting_header")`

<img src="../assets/central_plot.svg" alt="Completeness and timeliness of weekly reporting for the whole country">


### `r paste(i18n$t("overall_reporting_header"), paste0(numSem_W12[1], " (",yearSem_W12[1], ")"), i18n$t("to_week"), paste0(numSem_W12[12], " (", yearSem_W12[12], ")"))`

<img src="../assets/reporting_parent_sites.svg" alt="Overall completeness and timeliness of weekly reporting">

Row
-------------------------------------

###  `r paste(i18n$t("overall_review_header"), paste0(numSem_W12[1], " (",yearSem_W12[1], ")"), i18n$t("to_week"), paste0(numSem_W12[12], " (", yearSem_W12[12], ")"))`

<!-- <img src="../assets/administrative_report/review_plots.svg" alt="Overall completeness and timeliness of data review" height="87px" -->
<!--     width="100px"> -->

```{r dpi = 30}
knitr::include_graphics("../assets/review_plots.svg")
```


<script type="text/javascript">
(function() {
    var randomValue = Math.floor((Math.random() * 1000000) + 1);
    var images = document.getElementsByTagName("img");
    for (index in images) {
        var image = images[index];
        image.src = image.src + "?cacheResetValue=" + randomValue;
    }
})()
</script>

Row
-------------------------------------

### `r i18n$t("silent_sites_3_weeks_header")`

```{r}
DT::datatable(data = sites_no_report_3weeks,
              extensions = "Responsive",
              rownames = FALSE,
              options = list(
                columnDefs = list(list(responsivePriority = 1, targets = 0)),
                dom = 'tp'))
```

### `r i18n$t("silent_sites_8_weeks_header")`

```{r}
DT::datatable(data = sites_no_report_8weeks,
              extensions = "Responsive",
              rownames = FALSE,
              options = list(
                columnDefs = list(list(responsivePriority = 1, targets = 0)),
                dom = 'tp'))
```
