---
title: "Administrative summary"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    smooth_scroll: true
    css: style.css
    theme: cosmo
    self_contained: false
    mathjax: NULL
---

```{r setup, include=FALSE}
library(flexdashboard)

load("../assets/admin_report.RData")
```

<style>                     
.navbar {
  background-color:#5A0A69;
  border-color:black;
}
</style>

Row
-------------------------------------

### Completeness and timeliness of weekly reporting for the whole country

<img src="../assets/central_plot.svg" alt="Completeness and timeliness of weekly reporting for the whole country">


### Overall completeness and timeliness of weekly reporting from week `r paste0(min_week, " (", min_year, ")")` to `r paste0(max_week, " (", max_year, ")")`

<img src="../assets/reporting_parent_sites.svg" alt="Overall completeness and timeliness of weekly reporting">

Row
-------------------------------------

### Overall completeness and timeliness of data review at each level from week `r paste0(min_week, " (", min_year, ")")` to `r paste0(max_week, " (", max_year, ")")`

<img src="../assets/review_plots.svg" alt="Overall completeness and timeliness of data review">

<script type="text/javascript">
(function() {
    var randomValue = Math.floor((Math.random() * 1000000) + 1);
    var images = document.getElementsByTagName("img");
    for (index in images) {
        var image = images[index];
        image.src = image.src + "?cacheResetValue=" + randomValue;
    }
})()
</script>

Row
-------------------------------------

### Silent sites: reporting sites with no reports received for 8 weeks and longer

```{r}
DT::datatable(data = sites_no_report_8weeks,
          options = list(dom = 'tp'))
```

### Silent sites: reporting sites with no reports received for 3 weeks and longer

```{r}
DT::datatable(data = sites_no_report_3weeks,
          options = list(dom = 'tp'))
```
