---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    smooth_scroll: true
    css: style.css
    theme: cosmo
    self_contained: false
    mathjax: NULL
params:
  custom_title: "Epidemiological summary"
title: "`r params$custom_title`"
---

<style>                     
.navbar {
  background-color:#5A0A69;
  border-color:black;
}
#dashboard-container { 
  all: initial !important; 
}
</style>

Row {data-height=700}
-------------------------------------

### `r i18n$t("disease_charts_header")`

<img src="../assets/trends_occurrence.svg" alt="Trends of diseases having crossed thresholds in 12 previous weeks">

### `r i18n$t("disease_maps_header")`

<img src="../assets/map_occurrence.svg" alt="Maps of occurence of diseases crossing thresholds in the 2 previous weeks">

Row {data-height=400}
-------------------------------------

### `r i18n$t("disease_table_occurence_header")`

```{r}
DT::datatable(data = disease_occurrence_above_threshold,
              extensions = "Responsive",
              rownames = FALSE,
              options = list(
                columnDefs = list(list(responsivePriority = 1, targets = 0)),
                dom = 'tp'))
```

### `r i18n$t("disease_table_alerts_header")`
```{r}
DT::datatable(data = alert_list_D10,
              extensions = "Responsive",
              rownames = FALSE,
              options = list(
                columnDefs = list(list(responsivePriority = 1, targets = 0)),
                pageLength=5,
                dom = 'tp'))
```

Row
-------------------------------------

### `r paste0(i18n$t("disease_table_cumulative_header"),i18n$t("weekAbbr"),"1"," a ", i18n$t("weekAbbr"),numSem_W12[12])`

> `r paste0(yearPrevious,". ",i18n$t("representativeness"),nbRecValid_YR_previous,"/",nbExpected_YR_previous," (",percRecValid_YR_previous,"%)")`
> `r paste0(yearCurrent,". ",i18n$t("representativeness"),nbRecValid_YR,"/",nbExpected_YR," (",percRecValid_YR,"%)")`


```{r}
DT::datatable(data = cumulative_table,
               extensions = "Responsive",
               rownames = FALSE,
                options = list(
                  columnDefs = list(list(responsivePriority = 1, targets = 0)),
                  pageLength=length(diseases_name$disease[which(diseases_name$disease!="ALERT")]),
                  dom = 'tp'))
```
